---
title: "Homework 1"
subtitle: "Review on R, RStudio, and MLR"
---

```{r include=FALSE}

```

# Getting started

## This One Time

-   Go to our RStudio Server at <http://turing.cornellcollege.edu:8787/>

-   Go to your class folder you made named "STA363"

-   Create a new folder called *FirstInitial_Last_Initial_HW* with your initials. 

## Every Homework

Each of your assignments will begin with the following steps.

-   Finding the instructions on our website: [https://stats-tgeorge.github.io/STA363_AdvReg/](https://stats-tgeorge.github.io/STA363_AdvReg/)

-   Going to our RStudio Server at <http://turing.cornellcollege.edu:8787/>

-   Creating a new *project.* and giving it a sensible name such as *homework_1* and having that project in the course folder you created.

-   Create a new quarto document and give it a sensible name such as *hw1*.

-   In the `YAML` add the following (add what you don't have). The embed-resources component will make your final rendered `html` self-contained.

    ```{r}
#| label: yaml_example
#| eval: false
---
title: "Document title"
author: "my name"
format:
  html:
    embed-resources: true
---
    ```

# Instructions

Be sure to include the relevant R code as well as full sentences answering each of the questions (i.e. if I ask for the average, you can output the answer in R but **also** write a full sentence with the answer). Be sure to frequently save your files!

Data for the homework will be in the STA363_inst_files -> data folder.

# Exercises

All problems are from {{< var course.text >}}. Abbreviated BMLR. 

- Conceptual 1B
- Conceptual2a-d
- Conceptual Number 3
- Guided Number 3
 
Please do not give them new numbers. If you want to be brief, use a code such as C1B for the first problem. 

# Submission

When you are finished with your homework, be sure to Render the final document. Once rendered, you can download your file by:

-   Finding the .html file in your File pane (on the bottom right of the screen)
-   Click the check box next to the file
-   Click the blue gear above and then click "Export" to download
-   Submit your final html document to the respective assignment on [Moodle]({{< var course.moodle >}})



